\documentclass[line, margin, 10.5pt]{res}
\usepackage{hyperref}
\usepackage{textcomp}
\usepackage{tikz}
\usepackage[defblank]{paralist}
\usepackage[none]{hyphenat}
\usepackage{paralist}
\usepackage{enumitem}
\setlist[itemize]{leftmargin=*}

\addtolength{\topmargin}{-.25in}

% shrink left/right margins
\oddsidemargin -0.4in
\evensidemargin -0.4in
\textwidth     6.2in

% shrink top/bottom margins
\topmargin   -0.6in
\textheight  9.6in

\newcommand{\ExternalLink}{%
    \tikz[x=1.2ex, y=1.2ex, baseline=-0.05ex]{%
        \begin{scope}[x=1ex, y=1ex]
            \clip (-0.1,-0.1)
                --++ (-0, 1.2)
                --++ (0.6, 0)
                --++ (0, -0.6)
                --++ (0.6, 0)
                --++ (0, -1);
            \path[draw,
                line width = 0.5,
                rounded corners=0.5]
                (0,0) rectangle (1,1);
        \end{scope}
        \path[draw, line width = 0.5] (0.5, 0.5)
            -- (1, 1);
        \path[draw, line width = 0.5] (0.6, 1)
            -- (1, 1) -- (1, 0.6);
        }
    }

\begin{document}
\name{\Huge{Steve Greene}}

\begin{resume}

\section{\small MISSION}
Established software engineer specializing in Golang, Kubernetes, and cloud infrastructure, seeking to build and support scalable, high-performance distributed systems across clouds.

\section{\small CONTACT}
sgreene570@gmail.com \hfill (908) 300-1030 \\
\url{https://www.linkedin.com/in/sgreene570} \hfill Raleigh, NC \\
\url{https://github.com/sgreene570}

\section{\small EXPERIENCE}
{\bf \large{Confident Security}} \hfill \url{https://confident.security} \\
{\bf Senior Software Engineer} \hfill June 2025 - Present
\begin{itemize}
    \item Core contributor to \href{https://github.com/openpcc/openpcc}{OpenPCC}, a fully open-source implementation of Apple's Private Cloud Compute.
    \item Manage infrastructure for Confident Security's managed private AI offering (based on OpenPCC).
    \item Develop multi-layer Ubuntu-based hardened VM image to provide secure, attested AI inference.
    \item Add support for additional clouds and Trusted Execution Environments (TEE) to OpenPCC.
    \item Implement anonymous instrumentation and monitoring of production inference instances and workloads.
\end{itemize}

{\bf \large{Databricks}} \hfill \url{https://databricks.com} \\
{\bf Software Engineer (L4)} \hfill June 2023 - June 2025
\begin{itemize}
    \item Engineer on the Lakebase team alongside former bit.io engineers.
    \item Provided low-latency, high-throughput access to reverse-ETL data-serving tables in real time.
    \item Enabled asynchronous, reliable table creation via durable control plane reconcilers at scale.
    \item Orchestrated decoupled storage and compute machinery via bespoke Kubernetes controllers.
    \item Designed and implemented partitioned network infrastructure on AWS, Azure, and GCP.
    \item Provided guidance on Kubernetes design, operations, debugging, and scaling principles.
\end{itemize}

{\bf \large{bit.io}} \hfill (acquired by Databricks) \\
{\bf Software Engineer (L4)} \hfill July 2021 - June 2023
\begin{itemize}
    \item Engineer on the bit.io team, an affordable, easy to use serverless Postgres IaaS startup.
    \item Designed and implemented core Postgres pod-leasing controller for Kubernetes orchestration.
    \item Optimized cloud resource usage via fast and reliable database autoscaling.
    \item Deployed database infrastructure via cloud-provider managed Kubernetes clusters (e.g. GKE).
    \item Maintained developer experience (incl. CI/CD pipelines) to support rapid iteration.
\end{itemize}

{\bf \large{Red Hat}} \hfill \url{https://redhat.com} \\
{\bf Software Engineer} \hfill June 2020 - July 2021
\begin{itemize}
    \item Engineer on the OpenShift Container Platform's Network Edge (ingress) team.
    \item Deployed HAProxy-based ingress controllers via a Kubernetes operator.
    \item Contributed to upstream Kubernetes initiatives, such as CoreDNS \& External-DNS.
\end{itemize}

\section{\small EDUCATION}
{\bf Bachelor of Science in Computer Science} \hfill May 2020\\
Rochester Institute of Technology, Rochester, NY \hfill \url{https://rit.edu} \\
{\bf Activities:\bf} \href{https://csh.rit.edu}{Computer Science House}\\
{\bf Minor:\bf} Mathematics {\bf GPA:\bf} 3.43 (Honors Distinction)

\section{\small SKILLS}
\begin{compactdesc}
\item[Languages] \hfill \begin{inparaenum} {Golang, Scala, Python, PostgreSQL, Rust (learning), \LaTeX} \end{inparaenum}
\item[Operating Systems] \hfill \begin{inparaenum} {Ubuntu, Debian, Fedora, Docker, Podman, MacOS} \end{inparaenum}
\item[Infrastructure] \hfill \begin{inparaenum} {Kubernetes, GCP, AWS, Azure, Postgres, gRPC} \end{inparaenum}
\item[Tools] \hfill \begin{inparaenum} {Git, GitHub, Vim, JetBrains IDEs, Claude, Helm} \end{inparaenum}
\item[Recreation] \hfill \begin{inparaenum} {Disc golf, Bicycling, Bluegrass music} \end{inparaenum}
\item[Public Positions] \hfill \begin{inparaenum} {North Carolina Notary Public} \end{inparaenum}
\end{compactdesc}

\end{resume}
\end{document}
